Using reference models in variable selection \vspace{.1in}

### 2019-12-19 paper/ref_approach.tex
added sentence about RHS ref model for iterative proj

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity
against the false discovery rate.  In almost all of the bootstrapped
subsamples, the reference
model improves the selection both in terms of sensitivity and false
discovery rate. When $n=50$, we observe worse false
discovery rates, yet by a lower amount compared to the gain in
sensitivity. Again, we observe that the benefits are more evident as
the selection becomes more challenging (i.e., lower number of
observations).
The great performance of projpred in minimal subset selection is not
carried over for the complete variable selection with iterative
projpred, and the methods specifically designed for the complete 
variable selection perform better.
Figure \ref{fig:bodyfat_stability} shows the stability
results using the measure by
\cite{paper:stability}. The benefits of the reference model are here
marginal with only small improvements.

>>>>

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity
against the false discovery rate.  In almost all of the bootstrapped
subsamples, the reference
model improves the selection both in terms of sensitivity and false
discovery rate. When $n=50$, we observe worse false
discovery rates, yet by a lower amount compared to the gain in
sensitivity. Again, we observe that the benefits are more evident as
the selection becomes more challenging (i.e., lower number of
observations).
The great performance of projpred in minimal subset selection is not
carried over for the complete variable selection with iterative
projpred (even when changing the reference model into an full encompassing 
linear regression with regularised horseshoe prior), and the methods 
specifically designed for the complete variable selection perform better. 
Figure \ref{fig:bodyfat_stability} shows the stability
results using the measure by
\cite{paper:stability}. The benefits of the reference model are here
marginal with only small improvements.
